\vspace{-2cm}Development and Implementation of\\Novel Pair Value Encryption System

### 2021-06-09 paper/main.tex
updated works cited

\bibent
Halevi, Shai, et al. “Round-Optimal Secure Multi-Party Computation.” \textit{Journal of Cryptology}, vol. 34, no. 3, 2021, doi:10.1007/s00145-021-09382-3.

@@

\bibent
Tseng, Yi-Fan, et al. “Homomorphic Encryption Supporting Logical Operations.” \textit{Proceedings of the 2017 International Conference on Telecommunications and Communication Engineering - ICTCE '17}, 2017, doi:10.1145/3145777.3145789.

>>>>

\bibent
Halevi, Shai, et al. “Round-Optimal Secure Multi-Party Computation.” \textit{Journal of Cryptology}, vol. 34, no. 3, 2021.

@@

\bibent
Tseng, Yi-Fan, et al. “Homomorphic Encryption Supporting Logical Operations.” \textit{Proceedings of the 2017 International Conference on Telecommunications and Communication Engineering - ICTCE '17}, 2017.
